-!!!! Pay attention to the thetas across the specific and general in lis code     
# data from Li's article    
# item params from li's paper  
```{r}  
theta1 <- seq(-2,2, by = 1)  
theta2 <- seq(-2,2, by = 1)  
phi <- 0
a1 <- c(1.2,1.2,1,1,.8,.8)  
a2 <- c(1,1,.8,.8,1.2,1.2)  
c <- c(-1,-.6,-.2,.2,.6,1)  
```  


#2D Norm Dist  
```{r}
normal2d <- matrix(0, length(theta1), length(theta2))  
for (i in 1:length(theta1)) {  
  for (j in 1:length(theta2)) {  
    normal2d[i,j] = exp(-0.5*(theta1[i]^2+theta2[j]^2-2*phi*theta1[i]*theta2[j])/(1-phi*phi))  
  }  
}  
normal2d <- normal2d/sum(normal2d)  
```   
#MarginalPopDist (NormDist) here      
```{r}   

for (j in 1:length(theta1)) {      
  for (k in 1:length(theta2)){      
    marginalPopDist[j] <- marginalPopDist[j] + normal2d[j,k]      
  }      
}     
#sum(normal2d[1,])     
#sum(normal2d[,1])     
#marginalPopDist[1]     
```    
-As the three lines of code above indicate, all that is going in 'marginalPopDist' is each element is either a row or column sum of normal2d (which is )     
#Computing trace surface b4 the LW 2.0    
```{r}    
comp_TS <- function(theta1,    
                     theta2,    
                     a1,    
                     a2,    
                     c,    
                     normal2d,    
                     marginalPopDist) {    
  # Setting up matrices and vectors      
  nitems <- length(a1)      
  TS <- NULL      
  marginalT <- NULL      
  logistic <- NULL     
  for (i in 1:nitems) {                 
  tempj <- matrix(0, length(theta1), length(theta2))      
  tempk <- rep(0,length(theta1))       
  TS <- c(TS,list(tempj))      
  marginalT <- c(marginalT,list(tempk))      
  logistic <- c(logistic,list(tempk))      
  }    
  # This list will store both the calculated p (corect tline) and q(incorrect tline)    
  l <- list()    
for (i in 1:nitems) {      
  for (j in 1:length(theta1)) {      
    for (k in 1:length(theta2)){      
      TS[[i]][j,k] <- 1 / (1 + exp(-(a1[i]*theta1[j] + a2[i]*theta2[k] + (c[i]))))      
      marginalT[[i]][j] <- marginalT[[i]][j]+TS[[i]][j,k]*normal2d[j,k]      
    }      
    marginalT[[i]][j] <- marginalT[[i]][j]/marginalPopDist[j]      
  }      
}     
  for(i in 1:nitems) {    
    l[[i]] <- list()    
    l[[i]][[1]] <- numeric()    
    l[[i]][[2]] <- numeric()    
    l[[i]][[1]] <- 1-marginalT[[i]]    
    l[[i]][[2]] <- marginalT[[i]]    
  }    
  return(TS)    
}    
liCaiDat2 <- comp_TS(theta1,    
                     theta2,    
                     a1,    
                     a2,    
                     c,    
                     normal2d,    
                     marginalPopDist)    
    
    
nr <- 2   
ic <- c(1,1,2,2,3,3)   
TS_dataShape <- function(x, ic, nr, nQuad) {   
  l <- list()   
  ic_unique <- unique(ic)   
  item_index <- rep(seq(1,nr, by = 1), length(unique(ic)))   
  n_iter <- 0   
  for(i in 1:length(ic_unique)) {   
    l[[i]] <- list()   
    TF_index <- ic == ic_unique[i]   
    for(j in 1:length(TF_index[TF_index == TRUE])) {   
      n_iter <- n_iter+1   
      l[[i]][[j]] <- matrix(nrow = nQuad,   
                            ncol = nQuad)   
      l[[ic_unique[i]]][[j]] <- x[[n_iter]] #p   
    }   
  }   
     
  return(l)   
}   
    
liCaiDat2.1 <- TS_dataShape(liCaiDat2, ic, nr, 5)   
```     
- 1 - across all item clusters then all items w/ in each item cluster   
the issue is the different number of items in each item cluster    
   
 
# LW_2.3, still needs to add the integrtion (which is done)
# Though the multiplication needs to still be fixed
```{r}  
LW_2.3 <- function(x, nr, nQuad) {      
  l <- list()    
  # LW 2.0 step 1    
  for(k in 1:length(x)) { # i.e. for each item cluster    
     
  l[[k]] <- list()     
  l[[k]][[1]] <- list()  
  l[[k]][[2]] <- list()  
    
  l[[k]][[1]][[1]] <- matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)  
  l[[k]][[1]][[2]] <- 1 # correct for p  
  l[[k]][[2]][[1]] <- 1-matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)  
  l[[k]][[2]][[2]] <- 0 # correct for p  
    
  for(i in 2:length(x[[k]])) {   
    l[[k]] <- c(l[[k]],l[[k]])  
    ts_num <- length(l[[k]])  
        for(j in 1:ts_num) {    
          if(j <= ts_num/2) {   
        l[[k]][[j]][[1]] <- l[[k]][[j]][[1]]*x[[1]][[1]]  
        l[[k]][[j]][[2]] <- l[[k]][[j]][[2]]+1   
          }  
          else{  
            l[[k]][[j]][[1]] <- l[[k]][[j]][[1]]*(1-x[[k]][[1]])  
          }  
        }  
     
  }  
  } 
   
  l2 <- list() 
  temp <- list() 
   
  # looping over l to get temp[[k]][[2]] to contain unique sum scores 
  for(k in 1:length(l)) { 
    temp[[k]] <- list() 
    temp[[k]][[1]] <- numeric() # Vector for all Sum Scores across item clusters  
    for(i in 1:length(l[[k]])) { 
      temp[[k]][[1]][i] <- l[[k]][[i]][[2]]  
    } 
   temp[[k]][[2]] <- numeric() 
   temp[[k]][[3]] <- numeric() 
   temp[[k]][[2]] <- unique(temp[[k]][[1]]) 
   temp[[k]][[2]] <- sort(unique(temp[[k]][[1]])) 
   temp[[k]][[3]] <- data.frame(SS = temp[[k]][[2]], 
                                index = seq(1, length(temp[[k]][[2]]))) 
  
  } 
   
  for(k in 1:length(temp[[k]])){ 
    l2[[k]] <- list() 
    for(i in 1:length(temp[[k]][[2]])) { # indexing on SS +1 bc r cannot index on 0 
      l2[[k]][[i]] <- list() 
      l2[[k]][[i]][[1]] <- matrix(rep(0, 
                                 nQuad*nQuad), 
                             nrow = nQuad, 
                             ncol = nQuad) 
      l2[[k]][[i]][[2]] <- numeric() 
      l2[[k]][[i]][[2]] <- temp[[k]][[2]][i] 
       
  } 
  } 
   
  # the loop below combines lik 
    for(k in 1:length(l)) { 
    for(i in 1:length(l[[k]])) { 
      for(j in 1:nrow(temp[[k]][[3]])) { 
      if(l[[k]][[i]][[2]] == temp[[k]][[3]][[j,"SS"]]) 
      { 
        l2[[k]][[j]][[1]] <- l2[[k]][[j]][[1]]+l[[k]][[i]][[1]] 
      } 
    } 
  } 
  } 
  return(l2)  
} 
    
LC <- LW_2.3(liCaiDat2.1, 2, 5)    
``` 

# LW_2.4, adding in the fixed lik cal and integration
```{r}  
LW_2.4 <- function(x, nr, nQuad) {      
  l <- list()    
  # LW 2.0 step 1    
  for(k in 1:length(x)) { # i.e. for each item cluster    
     
  l[[k]] <- list()     
  l[[k]][[1]] <- list()  
  l[[k]][[2]] <- list()  
    
  l[[k]][[1]][[1]] <- matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)  
  l[[k]][[1]][[2]] <- 1 # correct for p  
  l[[k]][[2]][[1]] <- 1-matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)  
  l[[k]][[2]][[2]] <- 0 # correct for p  
    
  for(i in 2:length(x[[k]])) {   
    l[[k]] <- c(l[[k]],l[[k]])  
    ts_num <- length(l[[k]])  
        for(j in 1:ts_num) {    
          if(j <= ts_num/2) {   
        l[[k]][[j]][[1]] <- l[[k]][[j]][[1]]*x[[1]][[1]]  
        l[[k]][[j]][[2]] <- l[[k]][[j]][[2]]+1   
          }  
          else{  
            l[[k]][[j]][[1]] <- l[[k]][[j]][[1]]*(1-x[[k]][[1]])  
          }  
        }  
     
  }  
  } 
   
  l2 <- list() 
  temp <- list() 
   
  # looping over l to get temp[[k]][[2]] to contain unique sum scores 
  for(k in 1:length(l)) { 
    temp[[k]] <- list() 
    temp[[k]][[1]] <- numeric() # Vector for all Sum Scores across item clusters  
    for(i in 1:length(l[[k]])) { 
      temp[[k]][[1]][i] <- l[[k]][[i]][[2]]  
    } 
   temp[[k]][[2]] <- numeric() 
   temp[[k]][[3]] <- numeric() 
   temp[[k]][[2]] <- unique(temp[[k]][[1]]) 
   temp[[k]][[2]] <- sort(unique(temp[[k]][[1]])) 
   temp[[k]][[3]] <- data.frame(SS = temp[[k]][[2]], 
                                index = seq(1, length(temp[[k]][[2]]))) 
  
  } 
   
  for(k in 1:length(temp[[k]])){ 
    l2[[k]] <- list() 
    for(i in 1:length(temp[[k]][[2]])) { # indexing on SS +1 bc r cannot index on 0 
      l2[[k]][[i]] <- list() 
      l2[[k]][[i]][[1]] <- matrix(rep(0, 
                                 nQuad*nQuad), 
                             nrow = nQuad, 
                             ncol = nQuad) 
      l2[[k]][[i]][[2]] <- numeric() 
      l2[[k]][[i]][[2]] <- temp[[k]][[2]][i] 
       
  } 
  } 
   
  # the loop below combines lik 
    for(k in 1:length(l)) { 
    for(i in 1:length(l[[k]])) { 
      for(j in 1:nrow(temp[[k]][[3]])) { 
      if(l[[k]][[i]][[2]] == temp[[k]][[3]][[j,"SS"]]) 
      { 
        l2[[k]][[j]][[1]] <- l2[[k]][[j]][[1]]+l[[k]][[i]][[1]] 
      } 
    } 
  } 
    } 
  

  return(l)  
} 
    
LC <- LW_2.4(liCaiDat2.1, 2, 5)  
LC[[1]]
``` 
## trying to fix the within cluster lik cal
```{r}
likCalFun <- function(x, nQuad) { 
  
  LW_lik <- list() # IC-LW step-item (1- lik, 2 - ss)
  LW_final_step <- list()
for(k in 1:length(x)) { # i.e. for each item cluster    
     
  LW_lik[[k]] <- list() # list at the level of item clusters     
  LW_lik[[k]][[1]] <- list() # list for IC k lik cal iter 1
  LW_lik[[k]][[1]][[1]] <- list() # list for IC k lik cal iter 1 score 1
  LW_lik[[k]][[1]][[2]] <- list()# list for IC k lik cal iter 1 score 2
  LW_lik[[k]][[1]][[1]][[1]] <- matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)
  LW_lik[[k]][[1]][[1]][[2]] <- numeric()
  LW_lik[[k]][[1]][[1]][[2]] <- 1 # correct for p  
  LW_lik[[k]][[1]][[2]][[1]] <- 1-matrix(unlist(x[[k]][1]),  
                        nrow = 5,  
                        ncol = 5)  
  LW_lik[[k]][[1]][[2]][[2]] <- numeric()
  LW_lik[[k]][[1]][[2]][[2]] <- 0 # correct for p  
    
  for(i in 2:length(x[[k]])) {   
    LW_lik[[k]][[i]] <- c(LW_lik[[k]][[i-1]],
                     LW_lik[[k]][[i-1]])  
    ts_num <- length(LW_lik[[k]][[i]])  
        for(j in 1:ts_num) {    
          if(j <= ts_num/2) {   
        LW_lik[[k]][[i]][[j]][[1]] <- LW_lik[[k]][[i]][[j]][[1]]*x[[k]][[i]]  
        LW_lik[[k]][[i]][[j]][[2]] <- LW_lik[[k]][[i]][[j]][[2]]+1   
          }  
          else{  
            LW_lik[[k]][[i]][[j]][[1]] <- LW_lik[[k]][[i]][[j]][[1]]*(1-x[[k]][[i]])  
          }  
        }  
  } 
    max_likCal_iter <- length(LW_lik[[k]]) # keeping only the last iteration of the item cluster LW alg
  LW_lik[[k]] <- LW_lik[[k]][[max_likCal_iter]] 
} 
  unique_SS_lik <- list() # list to contain lik for unique SS
  temp <- list() # The purpose of temp is to create an index so that sum scores can be looped through, bc the SS = 0 index cannot be refrenced in loops.
   
  # looping over LW_lik to get temp[[k]][[2]] to contain unique sum scores 
  for(k in 1:length(LW_lik)) { 
    temp[[k]] <- list() 
    temp[[k]][[1]] <- numeric() # Vector for all Sum Scores across item clusters  
    for(i in 1:length(LW_lik[[k]])) { 
      temp[[k]][[1]][i] <- LW_lik[[k]][[i]][[2]]  
    } 
   temp[[k]][[2]] <- numeric() 
   temp[[k]][[3]] <- numeric() 
   temp[[k]][[2]] <- unique(temp[[k]][[1]]) 
   temp[[k]][[2]] <- sort(unique(temp[[k]][[1]])) 
   temp[[k]][[3]] <- data.frame(SS = temp[[k]][[2]], 
                                index = seq(1, length(temp[[k]][[2]]))) 
  
  }

  # first simply create empty matrices(i.e. 0's) so that they can be used to sum lik later 
    for(k in 1:length(temp[[k]])){ 
    unique_SS_lik[[k]] <- list() 
    for(i in 1:length(temp[[k]][[2]])) { # indexing on SS +1 bc r cannot index on 0 
      unique_SS_lik[[k]][[i]] <- list() 
      unique_SS_lik[[k]][[i]][[1]] <- matrix(rep(0, 
                                 nQuad*nQuad), 
                             nrow = nQuad, 
                             ncol = nQuad) 
      unique_SS_lik[[k]][[i]][[2]] <- numeric() 
      unique_SS_lik[[k]][[i]][[2]] <- temp[[k]][[2]][i] 
       
  } 
    } 
  
    # the loop below combines lik 
    for(k in 1:length(LW_lik)) { 
    for(i in 1:length(LW_lik[[k]])) { 
      for(j in 1:nrow(temp[[k]][[3]])) { 
      if(LW_lik[[k]][[i]][[2]] == temp[[k]][[3]][[j,"SS"]]) 
      { 
        unique_SS_lik[[k]][[j]][[1]] <- unique_SS_lik[[k]][[j]][[1]]+LW_lik[[k]][[i]][[1]] 
      } 
    } 
  } 
    }
  return(unique_SS_lik)
}

foo <- likCalFun(liCaiDat2.1, 5)
foo[[1]]
foo[[1]][[2]]
foo[[1]][[2]][[2]][[1]]+foo[[1]][[2]][[3]][[1]]
```
